Curve counting in genus one: elliptic singularities {\it \&} relative geometry

### 2019-06-27 EllipticSingularitiesSplitting.tex
Did some changes on this branch - whoops

\title[Reduced relative GW theory in genus 1]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
\author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
\date{\thismonthyear}

@@

We have produced a factorization
\[
\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,
\]
where the first map is flat and the second map is a logarithmic modification. The generic fiber can be interpreted geometrically.

{\bf \color{red} This lemma should be there, but the notation needs to be changed and the proof needs to be cleaned up. Luca?

@@

\begin{proof}
 All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve. By removing this factor, we see that when the dual graph is fixed, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$. We make the caveat here that(with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified). This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}. On the fiber boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches. Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree). This is patently the fan of a projective space.
\end{proof}}

@@

>>>>

\title[Curve counting in genus one: elliptic singularities and relative geometry]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
\author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
\date{\thismonthyear}

@@

We have produced a factorization
\begin{equation*}\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,
\end{equation*}
where the first map is flat and the second map is a logarithmic modification. $\widetilde\Dcal$ is a compactification of a torus bundle over $\widetilde\Ecal$ whose strata can be read off from the tropicalization; in particular, we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$. In fact, the generic fibre of $\widetilde\Dcal \to \widetilde\Ecal$ can be read off geometrically.

@@

\begin{proof}
 All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve. By removing this factor, we see that when the dual graph is fixed, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$. We make the caveat here that(with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified). This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}. On the fiber boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches. Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree). This is patently the fan of a projective space.
\end{proof}

@@

\subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} We now let $(X,Y)$ be a general smooth very ample pair. In \S \ref{} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.

This construction of the virtual fundamental class means that once we have established a recursion formula for $(\PP^N,H)$, it immediately pulls back to give a recursion formula for $(X,Y)$. To be more precise, Theorem \ref{theorem recursion} holds \emph{mutatis mutandis}, with the same values of $\lambda_\Dcal$. The computation of the splitting orders is exactly the same, and the recursive description of the boundary strata pulls back to give an entirely analogous description on $\VZ_{1,\alpha}(X|Y,\beta)$.
